Staged Abstract Interpreter

### 2018-01-03 paper.tex
references

@@

%% Bibliography
%\bibliography{bibfile}

>>>>

\section{Related Work}

\textbf{Abstract Compilation}. \citeauthor{Boucher:1996:ACN:647473.727587} present a closure generation 
technique to optimize the monovariant flow analysis \textit{0}-CFA for programs in continuation-passing style
\cite{Boucher:1996:ACN:647473.727587}.

\citeauthor{Johnson:2013:OAA:2500365.2500604} in their work also adopt the idea closure generation 
for an small-step abstracting abstract machine \cite{Johnson:2013:OAA:2500365.2500604}.

\textbf{Abstracting Abstract Machine}. Abstracting Definitional Interpreter \cite{darais2017abstracting}

Collapsing Towers of Interpreters\cite{Amin:2017:CTI:3177123.3158140}

@@

%% Bibliography
\bibliography{references}
